Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2018-12-19 paper/ms.tex
Add many orbits plot to paper

We now repeat the procedure but continuously changing the error in the assumed
midplane. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth minus
5\uth

\begin{figure*}
% \plotone{fig/something.pdf}
\caption{Caption.}
\label{fig:many_orbit_wrong_ref}
\end{figure*}

>>>>

We now repeat the procedure but continuously changing the error in the assumed
midplane. In Figure~\ref{fig:many_orbit_wrong_ref}, we report the 95\uth minus
5\uth percentile divided by the true action value for three different orbits.
The red orbit is exactly the same as in Figure~\ref{fig:one_orbit_wrong_ref},
and we also consider two more planar orbits with initial vertical velocities
of $30\,\kms$ (\Gus{orange}) and $10\,\kms$ (\Gus{blue}). For these two new
orbits, the true actions are $(J_r, L_z, J_z) = (37.9, -1520, 7.0)\,\actunit$
and $(40.4, -1520, 0.7)\,\actunit$ for the \Gus{orange} and \Gus{blue} orbits,
respectively. \Gus{Easy way to explain change in $J_r$?}

\begin{figure*}
\plotone{fig/many_orbits_schmactions.pdf}
\caption{Caption.}
\label{fig:many_orbit_wrong_ref}
\end{figure*}
